### 2020-01-28 ChapterResults/chapterResults.tex
Updated: 3x3 experiment diagram for results and minor tidy

\begin{figure}[!t]
	\begin{subfigure}{.5\textwidth}
		\begin{tikzpicture}[line cap=round,line join=round,>=triangle 45,x=1cm,y=1cm,scale=1.2]
		%	\clip(-3,-1.5) rectangle (3,3);
		\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.10000000149011612] (-1,-0.02) -- (1,-0.02) -- (1,-0.22) -- (-1,-0.22) -- cycle;
		\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.10000000149011612] (-0.02,2.5) -- (-0.02,0.5) -- (-0.22,0.5) -- (-0.22,2.5) -- cycle;
		\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.10000000149011612] (0.22,2.5) -- (0.22,0.5) -- (0.02,0.5) -- (0.02,2.5) -- cycle;
		\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.10000000149011612] (-2.5,0.22) -- (-0.5,0.22) -- (-0.5,0.02) -- (-2.5,0.02) -- cycle;
		\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.10000000149011612] (0.5,0.22) -- (2.5,0.22) -- (2.5,0.022) -- (0.5,0.022) -- cycle;
		\fill[line width=0.8pt,color=sim,fill=sim,fill opacity=0.1] (-3,3) -- (-3,-2) -- (3,-2) -- (3,3) -- cycle;
		\draw [line width=2pt] (-3,0)-- (3,0);
		\draw [line width=2pt] (0,3)-- (0,0);
		\draw [line width=0.8pt,color=rvwvcq] (-1,-0.02)-- (1,-0.02);
		\draw [line width=0.8pt,color=rvwvcq] (1,-0.02)-- (1,-0.22);
		\draw [line width=0.8pt,color=rvwvcq] (1,-0.22)-- (-1,-0.22);
		\draw [line width=0.8pt,color=rvwvcq] (-1,-0.22)-- (-1,-0.02);
		\draw [line width=0.8pt,color=rvwvcq] (-0.02,2.5)-- (-0.02,0.5);
		\draw [line width=0.8pt,color=rvwvcq] (-0.02,0.5)-- (-0.22,0.5);
		\draw [line width=0.8pt,color=rvwvcq] (-0.22,0.5)-- (-0.22,2.5);
		\draw [line width=0.8pt,color=rvwvcq] (-0.22,2.5)-- (-0.02,2.5);
		\draw [line width=0.8pt,color=rvwvcq] (0.22,2.5)-- (0.22,0.5);
		\draw [line width=0.8pt,color=rvwvcq] (0.22,0.5)-- (0.02,0.5);
		\draw [line width=0.8pt,color=rvwvcq] (0.02,0.5)-- (0.02,2.5);
		\draw [line width=0.8pt,color=rvwvcq] (0.02,2.5)-- (0.22,2.5);
		\draw (-1.5,2.5) node[anchor=center] {Server 0};
		\draw (1.5,2.5) node[anchor=center] {Server 1};
		\draw (0,-1) node[anchor=center] {Server 2};
		\draw [line width=0.8pt,color=rvwvcq] (-2.5,0.22)-- (-0.5,0.22);
		\draw [line width=0.8pt,color=rvwvcq] (-0.5,0.22)-- (-0.5,0.02);
		\draw [line width=0.8pt,color=rvwvcq] (-0.5,0.02)-- (-2.5,0.02);
		\draw [line width=0.8pt,color=rvwvcq] (-2.5,0.02)-- (-2.5,0.22);
		\draw [line width=0.8pt,color=rvwvcq] (0.5,0.22)-- (2.5,0.22);
		\draw [line width=0.8pt,color=rvwvcq] (2.5,0.22)-- (2.5,0.022);
		\draw [line width=0.8pt,color=rvwvcq] (2.5,0.022)-- (0.5,0.022);
		\draw [line width=0.8pt,color=rvwvcq] (0.5,0.022)-- (0.5,0.22);
		\draw [line width=0.8pt,color=rvwvcq] (-1.4,1.6)-- (-1.4,1.4);
		\draw [line width=0.8pt,color=rvwvcq] (-1.4,1.4)-- (-1.6,1.4);
		\draw [line width=0.8pt,color=rvwvcq] (-1.6,1.4)-- (-1.6,1.6);
		\draw [line width=0.8pt,color=rvwvcq] (-1.6,1.6)-- (-1.4,1.6);
		\draw [line width=0.8pt,color=rvwvcq] (1.6,1.6)-- (1.6,1.4);
		\draw [line width=0.8pt,color=rvwvcq] (1.6,1.4)-- (1.4,1.4);
		\draw [line width=0.8pt,color=rvwvcq] (1.4,1.4)-- (1.4,1.6);
		\draw [line width=0.8pt,color=rvwvcq] (1.4,1.6)-- (1.6,1.6);

@@

		\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.10000000149011612] (-2.5,0.22) -- (-2.3,0.22) -- (-2.3,0.02) -- (-2.5,0.02) -- cycle;

@@

		\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.10000000149011612] (0.5,-0.02) -- (2.5,-0.02) -- (2.5,-0.22) -- (0.5,-0.22) -- cycle;
		\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.10000000149011612] (-2.5,0.22) -- (-0.5,0.22) -- (-0.5,0.02) -- (-2.5,0.02) -- cycle;
		\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.10000000149011612] (0.5,0.22) -- (2.5,0.22) -- (2.5,0.022) -- (0.5,0.022) -- cycle;
		\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.10000000149011612] (-0.02,-0.5) -- (-0.02,-2.5) -- (-0.22,-2.5) -- (-0.22,-0.5) -- cycle;
		\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.10000000149011612] (0.22,-0.5) -- (0.22,-2.5) -- (0.02,-2.5) -- (0.02,-0.5) -- cycle;
		\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.10000000149011612] (-2.5,-0.022) -- (-0.5,-0.022) -- (-0.5,-0.22) -- (-2.5,-0.22) -- cycle;

@@

>>>>

\begin{figure}[!t]
	\begin{subfigure}{.5\textwidth}
		\begin{tikzpicture}[line cap=round,line join=round,>=triangle 45,x=1cm,y=1cm,scale=1.2]
		%	\clip(-3,-1.5) rectangle (3,3);
		\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (-1,-0.02) -- (1,-0.02) -- (1,-0.22) -- (-1,-0.22) -- cycle;
		\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (-0.02,2.5) -- (-0.02,0.5) -- (-0.22,0.5) -- (-0.22,2.5) -- cycle;
		\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (0.22,2.5) -- (0.22,0.5) -- (0.02,0.5) -- (0.02,2.5) -- cycle;
		\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (-2.5,0.22) -- (-0.5,0.22) -- (-0.5,0.02) -- (-2.5,0.02) -- cycle;
		\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (0.5,0.22) -- (2.5,0.22) -- (2.5,0.022) -- (0.5,0.022) -- cycle;
		\fill[line width=0.8pt,color=sim,fill=sim,fill opacity=0.1] (-3,3) -- (-3,-2) -- (3,-2) -- (3,3) -- cycle;
		\draw [line width=2pt] (-3,0)-- (3,0);
		\draw [line width=2pt] (0,3)-- (0,0);
		\draw [line width=0.8pt,color=rvwvcq] (-1,-0.02)-- (1,-0.02);
		\draw [line width=0.8pt,color=rvwvcq] (1,-0.02)-- (1,-0.22);
		\draw [line width=0.8pt,color=rvwvcq] (1,-0.22)-- (-1,-0.22);
		\draw [line width=0.8pt,color=rvwvcq] (-1,-0.22)-- (-1,-0.02);
		\draw [line width=0.8pt,color=rvwvcq] (-0.02,2.5)-- (-0.02,0.5);
		\draw [line width=0.8pt,color=rvwvcq] (-0.02,0.5)-- (-0.22,0.5);
		\draw [line width=0.8pt,color=rvwvcq] (-0.22,0.5)-- (-0.22,2.5);
		\draw [line width=0.8pt,color=rvwvcq] (-0.22,2.5)-- (-0.02,2.5);
		\draw [line width=0.8pt,color=rvwvcq] (0.22,2.5)-- (0.22,0.5);
		\draw [line width=0.8pt,color=rvwvcq] (0.22,0.5)-- (0.02,0.5);
		\draw [line width=0.8pt,color=rvwvcq] (0.02,0.5)-- (0.02,2.5);
		\draw [line width=0.8pt,color=rvwvcq] (0.02,2.5)-- (0.22,2.5);
		\draw (-1.5,2.5) node[anchor=center] {Server 0};
		\draw (1.5,2.5) node[anchor=center] {Server 1};
		\draw (0,-1) node[anchor=center] {Server 2};
		\draw [line width=0.8pt,color=rvwvcq] (-2.5,0.22)-- (-0.5,0.22);
		\draw [line width=0.8pt,color=rvwvcq] (-0.5,0.22)-- (-0.5,0.02);
		\draw [line width=0.8pt,color=rvwvcq] (-0.5,0.02)-- (-2.5,0.02);
		\draw [line width=0.8pt,color=rvwvcq] (-2.5,0.02)-- (-2.5,0.22);
		\draw [line width=0.8pt,color=rvwvcq] (0.5,0.22)-- (2.5,0.22);
		\draw [line width=0.8pt,color=rvwvcq] (2.5,0.22)-- (2.5,0.022);
		\draw [line width=0.8pt,color=rvwvcq] (2.5,0.022)-- (0.5,0.022);
		\draw [line width=0.8pt,color=rvwvcq] (0.5,0.022)-- (0.5,0.22);
		\draw [line width=0.8pt,color=rvwvcq] (-1.4,1.6)-- (-1.4,1.4);
		\draw [line width=0.8pt,color=rvwvcq] (-1.4,1.4)-- (-1.6,1.4);
		\draw [line width=0.8pt,color=rvwvcq] (-1.6,1.4)-- (-1.6,1.6);
		\draw [line width=0.8pt,color=rvwvcq] (-1.6,1.6)-- (-1.4,1.6);
		\draw [line width=0.8pt,color=rvwvcq] (1.6,1.6)-- (1.6,1.4);
		\draw [line width=0.8pt,color=rvwvcq] (1.6,1.4)-- (1.4,1.4);
		\draw [line width=0.8pt,color=rvwvcq] (1.4,1.4)-- (1.4,1.6);
		\draw [line width=0.8pt,color=rvwvcq] (1.4,1.6)-- (1.6,1.6);

@@

		\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (-2.5,0.22) -- (-2.3,0.22) -- (-2.3,0.02) -- (-2.5,0.02) -- cycle;

@@

		\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (0.5,-0.02) -- (2.5,-0.02) -- (2.5,-0.22) -- (0.5,-0.22) -- cycle;
		\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (-0.02,2.5) -- (-0.02,0.5) -- (-0.22,0.5) -- (-0.22,2.5) -- cycle;
		\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (0.22,2.5) -- (0.22,0.5) -- (0.02,0.5) -- (0.02,2.5) -- cycle;
		\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (-2.5,0.22) -- (-0.5,0.22) -- (-0.5,0.02) -- (-2.5,0.02) -- cycle;
		\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (0.5,0.22) -- (2.5,0.22) -- (2.5,0.022) -- (0.5,0.022) -- cycle;
		\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (-0.02,-0.5) -- (-0.02,-2.5) -- (-0.22,-2.5) -- (-0.22,-0.5) -- cycle;
		\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (0.22,-0.5) -- (0.22,-2.5) -- (0.02,-2.5) -- (0.02,-0.5) -- cycle;
		\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (-2.5,-0.022) -- (-0.5,-0.022) -- (-0.5,-0.22) -- (-2.5,-0.22) -- cycle;

@@

\begin{figure}[!t]
	\begin{tikzpicture}[line cap=round,line join=round,>=triangle 45,x=1cm,y=1cm]
	\fill[line width=0.8pt,color=sim,fill=sim,fill opacity=0.1] (-3,3) -- (-3,-6) -- (6,-6) -- (6,3) -- cycle;
	\draw [line width=2pt] (-3,0)-- (6,0);
	\draw [line width=2pt] (0,3)-- (0,-6);
	\draw [line width=2pt] (-3,-3)-- (6,-3);
	\draw [line width=2pt] (3,3)-- (3,-6);
	\draw (-1.5,2.5) node[anchor=center] {Server 0};
	\draw (1.5,2.5) node[anchor=center] {Server 1};
	\draw (4.5,2.5) node[anchor=center] {Server 2};
	\draw (-1.5,-0.5) node[anchor=center] {Server 3};
	\draw (1.5,-0.5) node[anchor=center] {Server 4};
	\draw (4.5,-0.5) node[anchor=center] {Server 5};
	\draw (-1.5,-3.5) node[anchor=center] {Server 6};
	\draw (1.5,-3.5) node[anchor=center] {Server 7};
	\draw (4.5,-3.5) node[anchor=center] {Server 8};

	%Injection volume
	% 4 -> 1
	\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (0.5,-0.02) -- (2.5,-0.02) -- (2.5,-0.22) -- (0.5,-0.22) -- cycle;
	% 0 -> 1
	\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (-0.02,2.5) -- (-0.02,0.5) -- (-0.22,0.5) -- (-0.22,2.5) -- cycle;
	% 1 -> 0
	\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (0.22,2.5) -- (0.22,0.5) -- (0.02,0.5) -- (0.02,2.5) -- cycle;
	% 0 -> 3
	\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (-2.5,0.22) -- (-0.5,0.22) -- (-0.5,0.02) -- (-2.5,0.02) -- cycle;
	% 1 -> 4
	\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (0.5,0.22) -- (2.5,0.22) -- (2.5,0.022) -- (0.5,0.022) -- cycle;
	% 3 -> 4
	\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (-0.02,-0.5) -- (-0.02,-2.5) -- (-0.22,-2.5) -- (-0.22,-0.5) -- cycle;
	% 4 -> 3
	\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (0.22,-0.5) -- (0.22,-2.5) -- (0.02,-2.5) -- (0.02,-0.5) -- cycle;
	% 3 -> 0
	\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (-2.5,-0.022) -- (-0.5,-0.022) -- (-0.5,-0.22) -- (-2.5,-0.22) -- cycle;

	% 5 -> 2
	\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (3.5,-0.02) -- (5.5,-0.02) -- (5.5,-0.22) -- (3.5,-0.22) -- cycle;
	% 6 -> 3
	\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (-2.5,-3.022) -- (-0.5,-3.022) -- (-0.5,-3.22) -- (-2.5,-3.22) -- cycle;
	% 7 -> 4
	\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (0.5,-3.022) -- (2.5,-3.022) -- (2.5,-3.22) -- (0.5,-3.22) -- cycle;
	% 8 -> 5
	\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (3.5,-3.022) -- (5.5,-3.022) -- (5.5,-3.22) -- (3.5,-3.22) -- cycle;
	% 2 -> 5
	\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (3.5,0.22) -- (5.5,0.22) -- (5.5,0.022) -- (3.5,0.022) -- cycle;
	% 3 -> 6
	\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (-2.5,-2.78) -- (-0.5,-2.78) -- (-0.5,-2.978) -- (-2.5,-2.978) -- cycle;
	% 4 -> 7
	\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (0.5,-2.78) -- (2.5,-2.78) -- (2.5,-2.978) -- (0.5,-2.978) -- cycle;
	% 5 -> 8
	\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (3.5,-2.78) -- (5.5,-2.78) -- (5.5,-2.978) -- (3.5,-2.978) -- cycle;
	% 1 -> 2
	\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (2.978,2.5) -- (2.978,0.5) -- (2.78,0.5) -- (2.78,2.5) -- cycle;
	% 4 -> 5
	\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (2.978,-0.5) -- (2.978,-2.5) -- (2.78,-2.5) -- (2.78,-0.5) -- cycle;
	% 6 -> 7
	\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (-0.02,-3.5) -- (-0.02,-5.5) -- (-0.22,-5.5) -- (-0.22,-3.5) -- cycle;
	% 7 -> 8
	\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (2.978,-3.5) -- (2.978,-5.5) -- (2.78,-5.5) -- (2.78,-3.5) -- cycle;
	% 7 -> 6
	\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (0.22,-3.5) -- (0.22,-5.5) -- (0.02,-5.5) -- (0.02,-3.5) -- cycle;
	% 2 -> 1
	\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (3.22,2.5) -- (3.22,0.5) -- (3.02,0.5) -- (3.02,2.5) -- cycle;
	% 5 -> 4
	\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (3.22,-0.5) -- (3.22,-2.5) -- (3.02,-2.5) -- (3.02,-0.5) -- cycle;
	% 8 -> 7
	\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (3.22,-3.5) -- (3.22,-5.5) -- (3.02,-5.5) -- (3.02,-3.5) -- cycle;

	% 4 -> 1
	\draw [line width=0.8pt,color=rvwvcq] (0.5,-0.02)-- (2.5,-0.02);
	\draw [line width=0.8pt,color=rvwvcq] (2.5,-0.02)-- (2.5,-0.22);
	\draw [line width=0.8pt,color=rvwvcq] (2.5,-0.22)-- (0.5,-0.22);
	\draw [line width=0.8pt,color=rvwvcq] (0.5,-0.22)-- (0.5,-0.02);

	% 5 -> 2
	\draw [line width=0.8pt,color=rvwvcq] (3.5,-0.02)-- (5.5,-0.02);
	\draw [line width=0.8pt,color=rvwvcq] (5.5,-0.02)-- (5.5,-0.22);
	\draw [line width=0.8pt,color=rvwvcq] (5.5,-0.22)-- (3.5,-0.22);
	\draw [line width=0.8pt,color=rvwvcq] (3.5,-0.22)-- (3.5,-0.02);

	% 0 -> 1
	\draw [line width=0.8pt,color=rvwvcq] (-0.02,2.5)-- (-0.02,0.5);
	\draw [line width=0.8pt,color=rvwvcq] (-0.02,0.5)-- (-0.22,0.5);
	\draw [line width=0.8pt,color=rvwvcq] (-0.22,0.5)-- (-0.22,2.5);
	\draw [line width=0.8pt,color=rvwvcq] (-0.22,2.5)-- (-0.02,2.5);

	% 1 -> 2
	\draw [line width=0.8pt,color=rvwvcq] (2.98,2.5)-- (2.98,0.5);
	\draw [line width=0.8pt,color=rvwvcq] (2.98,0.5)-- (2.78,0.5);
	\draw [line width=0.8pt,color=rvwvcq] (2.78,0.5)-- (2.78,2.5);
	\draw [line width=0.8pt,color=rvwvcq] (2.78,2.5)-- (2.98,2.5);

	% 1 -> 0
	\draw [line width=0.8pt,color=rvwvcq] (0.22,2.5)-- (0.22,0.5);
	\draw [line width=0.8pt,color=rvwvcq] (0.22,0.5)-- (0.02,0.5);
	\draw [line width=0.8pt,color=rvwvcq] (0.02,0.5)-- (0.02,2.5);
	\draw [line width=0.8pt,color=rvwvcq] (0.02,2.5)-- (0.22,2.5);

	% 2 -> 1
	\draw [line width=0.8pt,color=rvwvcq] (3.22,2.5)-- (3.22,0.5);
	\draw [line width=0.8pt,color=rvwvcq] (3.22,0.5)-- (3.02,0.5);
	\draw [line width=0.8pt,color=rvwvcq] (3.02,0.5)-- (3.02,2.5);
	\draw [line width=0.8pt,color=rvwvcq] (3.02,2.5)-- (3.22,2.5);

	% 0 -> 3
	\draw [line width=0.8pt,color=rvwvcq] (-2.5,0.22)-- (-0.5,0.22);
	\draw [line width=0.8pt,color=rvwvcq] (-0.5,0.22)-- (-0.5,0.02);
	\draw [line width=0.8pt,color=rvwvcq] (-0.5,0.02)-- (-2.5,0.02);
	\draw [line width=0.8pt,color=rvwvcq] (-2.5,0.02)-- (-2.5,0.22);

	% 1 -> 4
	\draw [line width=0.8pt,color=rvwvcq] (0.5,0.22)-- (2.5,0.22);
	\draw [line width=0.8pt,color=rvwvcq] (2.5,0.22)-- (2.5,0.022);
	\draw [line width=0.8pt,color=rvwvcq] (2.5,0.022)-- (0.5,0.022);
	\draw [line width=0.8pt,color=rvwvcq] (0.5,0.022)-- (0.5,0.22);

	% 2 -> 5
	\draw [line width=0.8pt,color=rvwvcq] (3.5,0.22)-- (5.5,0.22);
	\draw [line width=0.8pt,color=rvwvcq] (5.5,0.22)-- (5.5,0.022);
	\draw [line width=0.8pt,color=rvwvcq] (5.5,0.022)-- (3.5,0.022);
	\draw [line width=0.8pt,color=rvwvcq] (3.5,0.022)-- (3.5,0.22);

	% 3 -> 6
	\draw [line width=0.8pt,color=rvwvcq] (-2.5,-3.22)-- (-0.5,-3.22);
	\draw [line width=0.8pt,color=rvwvcq] (-0.5,-3.22)-- (-0.5,-3.02);
	\draw [line width=0.8pt,color=rvwvcq] (-0.5,-3.02)-- (-2.5,-3.02);
	\draw [line width=0.8pt,color=rvwvcq] (-2.5,-3.02)-- (-2.5,-3.22);

	% 4 -> 7
	\draw [line width=0.8pt,color=rvwvcq] (0.5,-3.22)-- (2.5,-3.22);
	\draw [line width=0.8pt,color=rvwvcq] (2.5,-3.22)-- (2.5,-3.022);
	\draw [line width=0.8pt,color=rvwvcq] (2.5,-3.022)-- (0.5,-3.022);
	\draw [line width=0.8pt,color=rvwvcq] (0.5,-3.022)-- (0.5,-3.22);

	% 5 -> 8
	\draw [line width=0.8pt,color=rvwvcq] (3.5,-3.22)-- (5.5,-3.22);
	\draw [line width=0.8pt,color=rvwvcq] (5.5,-3.22)-- (5.5,-3.022);
	\draw [line width=0.8pt,color=rvwvcq] (5.5,-3.022)-- (3.5,-3.022);
	\draw [line width=0.8pt,color=rvwvcq] (3.5,-3.022)-- (3.5,-3.22);

	% 3 -> 4
	\draw [line width=0.8pt,color=rvwvcq] (-0.02,-0.5)-- (-0.02,-2.5);
	\draw [line width=0.8pt,color=rvwvcq] (-0.02,-2.5)-- (-0.22,-2.5);
	\draw [line width=0.8pt,color=rvwvcq] (-0.22,-2.5)-- (-0.22,-0.5);
	\draw [line width=0.8pt,color=rvwvcq] (-0.22,-0.5)-- (-0.02,-0.5);

	% 4 -> 5
	\draw [line width=0.8pt,color=rvwvcq] (2.98,-0.5)-- (2.98,-2.5);
	\draw [line width=0.8pt,color=rvwvcq] (2.98,-2.5)-- (2.78,-2.5);
	\draw [line width=0.8pt,color=rvwvcq] (2.78,-2.5)-- (2.78,-0.5);
	\draw [line width=0.8pt,color=rvwvcq] (2.78,-0.5)-- (2.98,-0.5);

	% 6 -> 7
	\draw [line width=0.8pt,color=rvwvcq] (-0.02,-3.5)-- (-0.02,-5.5);
	\draw [line width=0.8pt,color=rvwvcq] (-0.02,-5.5)-- (-0.22,-5.5);
	\draw [line width=0.8pt,color=rvwvcq] (-0.22,-5.5)-- (-0.22,-3.5);
	\draw [line width=0.8pt,color=rvwvcq] (-0.22,-3.5)-- (-0.02,-3.5);

	% 7 -> 8
	\draw [line width=0.8pt,color=rvwvcq] (2.98,-3.5)-- (2.98,-5.5);
	\draw [line width=0.8pt,color=rvwvcq] (2.98,-5.5)-- (2.78,-5.5);
	\draw [line width=0.8pt,color=rvwvcq] (2.78,-5.5)-- (2.78,-3.5);
	\draw [line width=0.8pt,color=rvwvcq] (2.78,-3.5)-- (2.98,-3.5);

	% 4 -> 3
	\draw [line width=0.8pt,color=rvwvcq] (0.22,-0.5)-- (0.22,-2.5);
	\draw [line width=0.8pt,color=rvwvcq] (0.22,-2.5)-- (0.02,-2.5);
	\draw [line width=0.8pt,color=rvwvcq] (0.02,-2.5)-- (0.02,-0.5);
	\draw [line width=0.8pt,color=rvwvcq] (0.02,-0.5)-- (0.22,-0.5);

	% 5 -> 4
	\draw [line width=0.8pt,color=rvwvcq] (3.22,-0.5)-- (3.22,-2.5);
	\draw [line width=0.8pt,color=rvwvcq] (3.22,-2.5)-- (3.02,-2.5);
	\draw [line width=0.8pt,color=rvwvcq] (3.02,-2.5)-- (3.02,-0.5);
	\draw [line width=0.8pt,color=rvwvcq] (3.02,-0.5)-- (3.22,-0.5);

	% 3 -> 0
	\draw [line width=0.8pt,color=rvwvcq] (-2.5,-0.022)-- (-0.5,-0.022);
	\draw [line width=0.8pt,color=rvwvcq] (-0.5,-0.022)-- (-0.5,-0.22);
	\draw [line width=0.8pt,color=rvwvcq] (-0.5,-0.22)-- (-2.5,-0.22);
	\draw [line width=0.8pt,color=rvwvcq] (-2.5,-0.22)-- (-2.5,-0.022);

	% 7 -> 6
	\draw [line width=0.8pt,color=rvwvcq] (0.22,-3.5)-- (0.22,-5.5);
	\draw [line width=0.8pt,color=rvwvcq] (0.22,-5.5)-- (0.02,-5.5);
	\draw [line width=0.8pt,color=rvwvcq] (0.02,-5.5)-- (0.02,-3.5);
	\draw [line width=0.8pt,color=rvwvcq] (0.02,-3.5)-- (0.22,-3.5);

	% 8 -> 7
	\draw [line width=0.8pt,color=rvwvcq] (3.22,-3.5)-- (3.22,-5.5);
	\draw [line width=0.8pt,color=rvwvcq] (3.22,-5.5)-- (3.02,-5.5);
	\draw [line width=0.8pt,color=rvwvcq] (3.02,-5.5)-- (3.02,-3.5);
	\draw [line width=0.8pt,color=rvwvcq] (3.02,-3.5)-- (3.22,-3.5);

	% 3 -> 6
	\draw [line width=0.8pt,color=rvwvcq] (-2.5,-2.78)-- (-0.5,-2.78);
	\draw [line width=0.8pt,color=rvwvcq] (-0.5,-2.78)-- (-0.5,-2.978);
	\draw [line width=0.8pt,color=rvwvcq] (-0.5,-2.978)-- (-2.5,-2.978);
	\draw [line width=0.8pt,color=rvwvcq] (-2.5,-2.978)-- (-2.5,-2.78);

	% 4 -> 7
	\draw [line width=0.8pt,color=rvwvcq] (0.5,-2.78)-- (2.5,-2.78);
	\draw [line width=0.8pt,color=rvwvcq] (2.5,-2.78)-- (2.5,-2.978);
	\draw [line width=0.8pt,color=rvwvcq] (2.5,-2.978)-- (0.5,-2.978);
	\draw [line width=0.8pt,color=rvwvcq] (0.5,-2.978)-- (0.5,-2.78);

	% 5 -> 8
	\draw [line width=0.8pt,color=rvwvcq] (3.5,-2.78)-- (5.5,-2.78);
	\draw [line width=0.8pt,color=rvwvcq] (5.5,-2.78)-- (5.5,-2.978);
	\draw [line width=0.8pt,color=rvwvcq] (5.5,-2.978)-- (3.5,-2.978);
	\draw [line width=0.8pt,color=rvwvcq] (3.5,-2.978)-- (3.5,-2.78);

	% Server 0
	\draw [line width=0.8pt,color=rvwvcq] (-1.4,1.6)-- (-1.4,1.4);
	\draw [line width=0.8pt,color=rvwvcq] (-1.4,1.4)-- (-1.6,1.4);
	\draw [line width=0.8pt,color=rvwvcq] (-1.6,1.4)-- (-1.6,1.6);
	\draw [line width=0.8pt,color=rvwvcq] (-1.6,1.6)-- (-1.4,1.6);

	% Server 1
	\draw [line width=0.8pt,color=rvwvcq] (1.6,1.6)-- (1.6,1.4);
	\draw [line width=0.8pt,color=rvwvcq] (1.6,1.4)-- (1.4,1.4);
	\draw [line width=0.8pt,color=rvwvcq] (1.4,1.4)-- (1.4,1.6);
	\draw [line width=0.8pt,color=rvwvcq] (1.4,1.6)-- (1.6,1.6);

	% Server 2
	\draw [line width=0.8pt,color=rvwvcq] (4.6,1.6)-- (4.6,1.4);
	\draw [line width=0.8pt,color=rvwvcq] (4.6,1.4)-- (4.4,1.4);
	\draw [line width=0.8pt,color=rvwvcq] (4.4,1.4)-- (4.4,1.6);
	\draw [line width=0.8pt,color=rvwvcq] (4.4,1.6)-- (4.6,1.6);

	% Server 3
	\draw [line width=0.8pt,color=rvwvcq] (-1.4,-1.6)-- (-1.4,-1.4);
	\draw [line width=0.8pt,color=rvwvcq] (-1.4,-1.4)-- (-1.6,-1.4);
	\draw [line width=0.8pt,color=rvwvcq] (-1.6,-1.4)-- (-1.6,-1.6);
	\draw [line width=0.8pt,color=rvwvcq] (-1.6,-1.6)-- (-1.4,-1.6);

	% Server 4
	\draw [line width=0.8pt,color=rvwvcq] (1.6,-1.6)-- (1.6,-1.4);
	\draw [line width=0.8pt,color=rvwvcq] (1.6,-1.4)-- (1.4,-1.4);
	\draw [line width=0.8pt,color=rvwvcq] (1.4,-1.4)-- (1.4,-1.6);
	\draw [line width=0.8pt,color=rvwvcq] (1.4,-1.6)-- (1.6,-1.6);

	% Server 5
	\draw [line width=0.8pt,color=rvwvcq] (4.6,-1.6)-- (4.6,-1.4);
	\draw [line width=0.8pt,color=rvwvcq] (4.6,-1.4)-- (4.4,-1.4);
	\draw [line width=0.8pt,color=rvwvcq] (4.4,-1.4)-- (4.4,-1.6);
	\draw [line width=0.8pt,color=rvwvcq] (4.4,-1.6)-- (4.6,-1.6);

	% Server 6
	\draw [line width=0.8pt,color=rvwvcq] (-1.4,-4.6)-- (-1.4,-4.4);
	\draw [line width=0.8pt,color=rvwvcq] (-1.4,-4.4)-- (-1.6,-4.4);
	\draw [line width=0.8pt,color=rvwvcq] (-1.6,-4.4)-- (-1.6,-4.6);
	\draw [line width=0.8pt,color=rvwvcq] (-1.6,-4.6)-- (-1.4,-4.6);

	% Server 7
	\draw [line width=0.8pt,color=rvwvcq] (1.6,-4.6)-- (1.6,-4.4);
	\draw [line width=0.8pt,color=rvwvcq] (1.6,-4.4)-- (1.4,-4.4);
	\draw [line width=0.8pt,color=rvwvcq] (1.4,-4.4)-- (1.4,-4.6);
	\draw [line width=0.8pt,color=rvwvcq] (1.4,-4.6)-- (1.6,-4.6);
